Machine Learning Approaches for Ammonia Volatilization Prediction after Manure Application

### 2024-05-23 manuscript.qmd
commenting and minor corrections

```{r}
library ("readxl")
library ("ggplot2") # version 3.4.4
library ("gridExtra") # version 2.3
library ("dplyr") # version 1.1.2      
library ("paletteer") # version 1.4.0
library ("tibble") # version 3.2.1
library ("tidyr") # version 1.3.0
library ("ALFAM2") # version 3.7
library ("randomForest") # version 4.7.1.1
library ("xgboost") # version 1.7.6.1
library ("glmnet") # version 4.1.8
library ("treeshap") # version 0.3.1
library ("shapviz") # version 0.9.3
library ("kableExtra") # version 1.3.4
```

```{r}
axis_text_size = 22 
axis_title_size = 26
title_size = 26

@@

## Alfam2

@@

```{r, fig.width = 10, fig.height = 12}
alfam2_predictions %>%
    mutate (app.mthd = recode (app.mthd, "bc" = "Broadcast", "bsth" = "Trailing hose", "ts" = "Trailing shoe", "os" = "Open slot injection")) %>%
    mutate (app.mthd = factor (app.mthd, levels = c ("Broadcast", "Trailing hose", "Trailing shoe", "Open slot injection"))) %>%
    mutate (residuals = truth_er - er) %>%
    pivot_longer (cols = c ("er", "truth_er", "residuals")) %>%
    mutate (name = recode (name, "er" = "prediction", "truth_er" = "truth")) %>%
    mutate (name = factor (name, levels = c ("truth", "prediction", "residuals"))) %>%
    ggplot () +
        geom_boxplot (aes (x = country, y = value, fill = name)) +
        geom_hline (yintercept = 0, linetype = 2) +
        facet_wrap (~ app.mthd, ncol = 1) +
        ylab ("Relative 72h cum. emission or residual") +
        labs (fill = "") +
        theme (legend.position = "bottom",
               axis.title.y = element_text (margin = ggplot2::margin (r = 30)),
               strip.text.x = element_text(margin = ggplot2::margin(t = 8, b = 8, r = 0, l = 0)))
```

@@

@@

@@

@@

```{r}
predictions_of_all_methods %>% head
```

@@

@@

@@

    mutate_if (is.numeric, round, digits = 3)

@@

    mutate (variation = (1 - abs(value) / abs(value [method == "alfam2"])) * 100, .by = c(name, dataset)) %>%

@@

```{r}
df_importance_rf %>%
    arrange (desc (`%IncMSE`)) %>%
    head (n = 10) %>% kable ()
```

@@

```{r}
df_importance_xgb %>%
    arrange (desc (Gain)) %>%
    head (n = 10) %>% kable ()
```

@@

## Alfam2

@@

@@

plot = ggplot (data_tmp) +
    geom_histogram (aes (efficacy_xgboost)) +
    facet_wrap (~ tan.app + app.rate + group_rain) +
    xlab ("Efficacy") +
    ylab ("Number of predictions") +
    theme (axis.title.y = element_text (margin = ggplot2::margin (r = 20)),
           strip.text.x = element_text(margin = ggplot2::margin(t = 8, b = 8, r = 0, l = 0)),
           strip.text = element_text (size = 20))

@@

```{r}
data_scenarios %>%
  filter (! (app.mthd == "bc" & incorp == "none")) %>%
  summarise (mean_rf = mean (efficacy_random_forest), 
             mean_alfam2 = mean (efficacy_alfam2), 
             mean_gbf = mean (efficacy_xgboost), 
             mean_lasso = mean (efficacy_lasso), .by = c ('app.mthd')) %>%
  kable()
```

>>>>

```{r}
library ("readxl") # version 1.4.3
library ("ggplot2") # version 3.4.4
library ("gridExtra") # version 2.3
library ("dplyr") # version 1.1.2      
library ("paletteer") # version 1.4.0
library ("tibble") # version 3.2.1
library ("tidyr") # version 1.3.0
library ("ALFAM2") # version 3.7
library ("randomForest") # version 4.7.1.1
library ("xgboost") # version 1.7.6.1
library ("glmnet") # version 4.1.8
library ("treeshap") # version 0.3.1
library ("shapviz") # version 0.9.3
library ("kableExtra") # version 1.3.4
```

```{r, include = FALSE}
axis_text_size = 22 
axis_title_size = 26
title_size = 26

@@

## ALFAM2

Predictions of emissions using the ALFAM2 model.

@@

@@

Predictions of emissions using random forest.

@@

Predictions of emissions using gradient boosting.

@@

Predictions of emissions using Lasso regression.

@@

```{r}
predictions_of_all_methods %>% head %>% mutate_if (is.numeric, round, digits = 1) %>% kable
```

@@

Comparison of residual for the calibration and evaluation subsets.

@@

Comparison of residual for the evaluation subset.

@@

    mutate_if (is.numeric, round, digits = 2)

@@

    mutate (variation = (1 - abs(value) / abs(value [method == "alfam2"])) * 100, .by = c(name, dataset)) %>%
    mutate (variation = round (variation, digits = 1)) %>%
    mutate (value = round (value, digits = 1)) %>%

@@

```{r}
df_importance_rf %>%
    arrange (desc (`%IncMSE`)) %>%
    mutate_if (is.numeric, round, digits = 2) %>%
    kable ()
```

@@

```{r}
df_importance_xgb %>%
    arrange (desc (Gain)) %>%
    mutate_if (is.numeric, round, digits = 2) %>%
    kable ()
```

@@

## ALFAM2

@@

Scenarios for which xgboost predicted a positive efficacy:

@@

plot = ggplot (data_tmp) +
    geom_histogram (aes (efficacy_xgboost)) +
    facet_wrap (~ tan.app + app.rate + group_rain) +
    xlab ("Efficacy") +
    ylab ("Number of predictions") +
    theme (axis.title.y = element_text (margin = ggplot2::margin (r = 20)),
           strip.text.x = element_text(margin = ggplot2::margin(t = 8, b = 8, r = 0, l = 0)),
           strip.text = element_text (size = 24))

@@

```{r}
data_scenarios %>%
  filter (! (app.mthd == "bc" & incorp == "none")) %>%
  summarise (mean_rf = mean (efficacy_random_forest), 
             mean_alfam2 = mean (efficacy_alfam2), 
             mean_gbf = mean (efficacy_xgboost), 
             mean_lasso = mean (efficacy_lasso), .by = c ('app.mthd')) %>%
  mutate_if (is.numeric, round, digits = 1) %>%
  kable()
```
